\chapter*{Acknowledgements}

% Academic
I'd first like to thank my supervisor Fabrizio Salvatore, for being exactly as hands-on and hands-off as I needed, when I needed it, and without whose help, guidance and faith I wouldn't have been able to do this. Thanks to all at the FLC group at DESY in Hamburg, but especially to Katja Kr\"{u}ger, Adrian Irles-Quiles (now at LAL Orsay), and R\'{e}mi Et\'{e}. Also thanks to the members of the IDEA collaboration, especially Romualdo Santoro. Thanks also the CLIDdp collaboration, but especially Yixuan Zhang and Victoria Martin. \newline

% Funding
I would like to thank the UK's Science and Technology Funding Council for supporting my studentship and providing me with the funding to perform this research. Thanks also to Linear Collider UK for providing vital funding for travel for the linear collider community in the UK. \newline

% AIDA-2020
I would also like to thank the whole AIDA-2020 collaboration for providing the working environment for a large portion of the work of this thesis and always scheduling their annual meetings in sunny countries with good food. Special thanks to all of the members of Work Package 5 for their support and expertise, and to David Cussans and Matthew Wing for their leadership and organisation of the activities within the group.

Similarly, I would like to thank all of the organisers of the Beam Telescopes and Test Beams workshop for providing a forum for researchers to discuss our work and learn from each other. \newline

% Personal
Finally, thanks to my highschool physics teachers Mr Coombes and Mr Thomas, who nurtured my early love for physics. I'd like to take this opportunity to apologise for never doing my homework, and hope that this thesis makes up for it.