\documentclass[
11pt, % Main document font size
a4paper,
oneside,
]{scrartcl}

\pagestyle{empty}
\usepackage{hyperref}
\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=magenta,      
    urlcolor=blue,
}

\begin{document}


\section*{Summary of changes}
Following the comments of the examiners and our discussion during the viva, I have implemented the following changes to my thesis:

\begin{itemize}
	\item Fixed spelling and grammatical errors throughout.
	\item Rephrased and recontextualised some points for clarity and precision, according to examiners' suggestions.
	\item Added citations in Chapter 1 to support the description and discussion of the Standard Model which was previously unsupported.
	\item Added citations for figures in Chapter 1 that were previously not attributed.
	\item Added section in Chapter 2 on existing online monitoring and data quality monitoring solutions, justifying the motivation for DQM4hep in the context of existing tools.
	\item Added ``heatmap'' of detector in Chapter 4, showing the mean ADCs of the calibration runs, as a way of potentially identifying geometric patterns by eye. Also added text commenting that this is a good demonstration of easily creating ad hoc analysis plots using DQM4hep
	\item Added summary figure of raw ADCs for all channels of the detector in Chapter 4, demonstrating that the histograms are approximately Gaussian.
	\item Replaced Figure 5.9 with the correct plot and updated the caption appropriately.
	\item Fixed formatting errors and inconsistencies in the bibliography, especially ensuring that all authors are given in the format ``F Surname''. Entries with a large number of authors are now credited either by their collaboration, or by the name of the first author \textit{et al}.
\end{itemize}

If an exact account of all changes is required, the Github repository I used to backup and store my thesis provides a list of all differences between the version submitted for the viva, and the corrected version. This can be found \href{https://github.com/tcoates3/thesis/compare/viva...corrections}{here}.

\end{document}
